---
title: "HW11"
author: '106022103'
date: "2021/5/8"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assist
+ `106000199`
  + Helped me how to get factor names in data.frame.
  + Disscussed about the Q2.a, which visualization should take.
  
  
  
## Set up 

### import libary

```{r import, message=FALSE, warning=FALSE}
library(ggplot2)
require(qqplotr)
library(plyr)
library(gridExtra)
library(ggcorrplot)
library(magrittr)
library(ggpubr)
```

## Q1

### (a) Let’s dig into what regression is doing to compute model fit

Because `interactive_regression` can't run in Rmarkdown knit, we have to run these commands in console and save the variables `pts`.


```r
pts <- interactive_regression() 
saveRDS(pts, file = "W:/Rtmp/pts.rds")
```

#### i. Plot Scenario 2, storing the returned points: `pts <- interactive_regression_rsq()`

```{r}
pts <- readRDS(file = "W:/Rtmp/pts1.rds")
```



#### ii. Run a linear model of x and y points to confirm the R2 value reported by the simulation:

```{r}
regr <- lm(y ~ x, data=pts)
summary(regr)
```

#### iii. Add line segments to the plot to show the regression residuals (errors) as follows:  

+ Get values of y( regression line’s estimates of y, given x): y_hat <- regr$fitted.values  
+ Add segments: segments(pts$x, pts$y, pts$x, y_hat, col="red", lty="dotted")  

```{r}
pts_regr <- lm(y~x, data=pts)
y_hat <- pts_regr$fitted.values

plot(pts)
abline(pts_regr)
segments(pts$x, pts$y, pts$x, y_hat, col="red", lty="dotted")
```





#### iv. Use only pts$x, pts$y, y_hat and mean(pts$y) to compute SSE, SSR and SST, and verify R2 

```{r}
SSE <- sum((pts$y-y_hat)^2)
SSR <- sum((y_hat-mean(pts$y))^2)
SST <-  SSE + SSR
R2 <- SSR/SST
cat(sprintf("SSE\tSSR\tSST\tR^2\n%.2f\t%.2f\t%.2f\t%.2f\n", SSE, SSR, SST, R2))
```

### (b) Comparing scenarios 1 and 2, which do we expect to have a stronger $R^2$ ?

**ANSWER:** scenarios 1.


### (c) Comparing scenarios 3 and 4, which do we expect to have a stronger $R^2$ ?

**ANSWER:** scenarios 3.

### (d) Comparing scenarios 1 and 2, which do we expect has bigger/smaller SSE, SSR, and SST?

> (do not compute SSE/SSR/SST here – just provide your intuition)
 
**ANSWER:** scenarios 2.


### (e) Comparing scenarios 3 and 4, which do we expect has bigger/smaller SSE, SSR, and SST?

> (do not compute SSE/SSR/SST here – just provide your intuition)

**ANSWER:** scenarios 4.








## Q2

### Read File

```{r read file}
auto <- read.table("data/auto-data.txt", header=FALSE, na.strings = "?")
names(auto) <- c("mpg", "cylinders", "displacement", "horsepower", "weight", 
                 "acceleration", "model_year", "origin", "car_name")
```


### (a) data explore


#### i.  Visualize the data in any way

##### Preprocess
```{r}
cylinder_freq <- as.data.frame(table(auto$cylinders))
origin_freq <- as.data.frame(table(auto$origin))
year_freq <- as.data.frame(table(auto$model_year))

names(cylinder_freq) <- c("cylinder","Freq")
names(origin_freq) <- c("origin","Freq")
names(year_freq) <- c("model_year","Freq")

sum(is.na(auto)) # How many na values
auto <- auto[complete.cases(auto), ] # remove missing value

auto[,'origin']<-factor(auto[,'origin']) # convert to factor
auto[,'car_name']<-factor(auto[,'car_name']) # convert to factor

auto_value <- auto[,-8:-9] # drop the class data
corr <- round(cor(auto_value), 2)
p.mat <- cor_pmat(auto_value)
```

Since there are no so many missing values, so I decided to just remove them.

##### Pie Chart  

```{r}
p1 <- ggplot(data=cylinder_freq) +
    geom_bar(aes(x=factor(1),
                 y=Freq,
                 fill=cylinder),
             stat = "identity") +
    coord_polar("y", start=0) + 
    scale_fill_brewer(palette="Blues") +
    theme_void() # remove background

p2 <- ggplot(data=origin_freq) +
    geom_bar(aes(x=factor(1),
                 y=Freq,
                 fill=origin),
             stat = "identity") +
    coord_polar("y", start=0) + 
    scale_fill_brewer(palette="Dark2") +
    theme_void() # remove background

p3 <- ggplot(data=year_freq) +
    geom_bar(aes(x=factor(1),
                 y=Freq,
                 fill=model_year),
             stat = "identity") +
    coord_polar("y", start=0) + 
    scale_fill_grey() +
    theme_void() # remove background

grid.arrange(p1,p2,p3,nrow=1,ncol=3)
```




##### Violin plot  
  
```{r}
p4 <- ggplot(auto, aes(x=origin, y=displacement, color=origin)) + 
  geom_violin() + 
  coord_flip() + 
  theme(legend.position="none")

p5 <- ggplot(auto, aes(x=origin, y=horsepower, color=origin)) + 
  geom_violin() + 
  coord_flip() + 
  theme(legend.position="none")

p6 <- ggplot(auto, aes(x=origin, y=weight, color=origin)) + 
  geom_violin() + 
  coord_flip() + 
  theme(legend.position="none")

p7 <- ggplot(auto, aes(x=origin, y=acceleration, color=origin)) + 
  geom_violin() + 
  coord_flip() + 
  theme(legend.position="none")

p8 <- ggplot(auto, aes(x=origin, y=model_year, color=origin)) + 
  geom_violin() + 
  coord_flip() + 
  theme(legend.position="none")



grid.arrange(p4,p5,p6,p7,p8, nrow=1,ncol=5)
```

#### ii. Report a correlation table of all variables

###### Corr matrix

```{r}
ggcorrplot(corr, hc.order = TRUE,
           type = "lower", p.mat = p.mat, lab = TRUE)
```



#### iii. which variables seem to relate to mpg?

**ANSWER:** Take $0.7$ as the threshold value, `mpg` is related to `displacement`, `cylinders`, `weight`, `horsepower`.


#### iv. Which relationships might not be linear?
```{r}
# ref.7
# 將相關係數與p-value矩陣轉換成data frame的函數
flattenCorrMatrix <- function(cormat) {
  ut <- upper.tri(cormat) # Lower and Upper Triangular Part of a Matrix
  data.frame(
    var1 = rownames(cormat)[row(cormat)[ut]],
    var2 = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut]
  )
}
cor_table <- flattenCorrMatrix(corr)
```




**ANSWER:** Take $0.5$ as the threshold value, the following relationships may not be linear:

```{r}
cor_table %>% dplyr::filter(abs(cor) < 0.5)
```
Take $0.3$ as the threshold value, the following relationships may not be linear:

```{r}
cor_table %>% dplyr::filter(abs(cor) < 0.3)
```


#### v. Are there any pairs of independent variables that are highly correlated (r > 0.7)?

**ANSWER:** The following relationships are highly correlated:

```{r}
cor_table %>% dplyr::filter(abs(cor) >0.7)
```



### (b) linear regression model

```{r}
regr_all <- lm(mpg~., data = auto_value)
summary(regr_all)
```
#### i. Which independent variables have a ‘significant’ relationship with mpg at 1% significance?

**ANSWER:**  The `weight`, `model_year` have a ‘significant’ relationship with mpg at 1% significance.

#### ii. Is it possible to determine which independent variables are the most effective at increasing mpg? If so, which ones, and if not, why not? (hint: units!)  

**ANSWER:** It seems `weight`, `model_year` are the most effective variables at increasing `mpg`.



### (c)


#### i. Create fully standardized regression results: are these slopes easier to compare?


```{r}
auto_value_std <- data.frame(scale(auto_value))
auto_value_std$origin <-auto$origin
regr_std <- lm(mpg~., data = auto_value_std)
summary(regr_std)
```
**ANSWER:** The `origin` should not be standardize, and the slope are easier to compare with each other.  

#### ii. Regress mpg over each nonsignificant independent variable, individually. Which ones become significant when we regress mpg over them individually?


```{r}
regr_cylinders <- lm(mpg ~ cylinders, data = auto_value_std)
regr_horsepower <- lm(mpg ~ horsepower, data = auto_value_std)
regr_acceleration <- lm(mpg ~ acceleration, data = auto_value_std)
summary(regr_cylinders)
summary(regr_horsepower)
summary(regr_acceleration)
```

**ANSWER:** When we regress `mpg` over each `cylinders`, `horsepower` and `acceleration`, individually, all nonsignificant independent variable become **significant**!

#### iii. Plot the density of the residuals: are they normally distributed and centered around zero?

```{r}
# The function to plot qqplot
norm_qq_ggplot <- function(values){
  text <- substitute(values)
  df <- data.frame(value=values)
  gg <- ggplot(data = df, mapping = aes(sample = value)) +
      stat_qq_band() +
      stat_qq_line() +
      stat_qq_point() +
      labs(x = "Theoretical Quantiles", y = "Sample Quantiles", title = "QQplot")
  gg
}


density_hist_plot <- function(values){
  p <- ggplot(mapping = aes(values)) +
    geom_histogram(mapping = aes(y = stat(density))) +
    geom_density(color = "red", size = 1) +
    labs(title = "density plot")
  p
}

# combine two plots
density_qq_plot <- function(values){
  text <- substitute(values)
  p1 <- norm_qq_ggplot(values)
  p2 <- density_hist_plot(values)
  figure <- ggarrange(p1,p2)
  annotate_figure(figure,top = text_grob(text, color = "red", face = "bold", size = 14))
  # grid.arrange(p1,p2, nrow=1,ncol=2)
}
```



```{r, message=FALSE, warning=FALSE}
density_qq_plot(regr_all$residuals)
density_qq_plot(regr_std$residuals)
density_qq_plot(regr_cylinders$residuals)
density_qq_plot(regr_horsepower$residuals)
density_qq_plot(regr_acceleration$residuals)
```

**ANSWER:** All residuals are normally distributed and centered around zero.

## Reference Link

+ [Counting the number of elements with the values of x in a vector](https://stackoverflow.com/questions/1923273/counting-the-number-of-elements-with-the-values-of-x-in-a-vector)
+ [R visulize](https://bookdown.org/jefflinmd38/r4biost/dataviz.html)
+ [Visualization of a correlation matrix using ggplot2](http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2)
+ [Impute Missing Value](https://rpubs.com/skydome20/R-Note10-Missing_Value)
+ [How to convert integer to factor in R?](https://stackoverflow.com/questions/31165015/how-to-convert-integer-to-factor-in-r/31165259)
+ [ggplot2 violin plot](http://www.sthda.com/english/wiki/ggplot2-violin-plot-quick-start-guide-r-software-and-data-visualization#change-the-legend-position)
+ [Regularized Regression](https://www.jamleecute.com/regularized-regression-ridge-lasso-elastic/)
+ [ggplot2 - Easy Way to Mix Multiple Graphs on The Same Page](http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/81-ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page/)
+ [Extract variable names from list or vector in R](https://stackoverflow.com/questions/42227416/extract-variable-names-from-list-or-vector-in-r)