---
title: "HW15"
author: '106022103'
date: "2021/6/5"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE, warning = FALSE)
```

### import libary
```{r}
library(openxlsx) # read.xlsx()
library(ggplot2) 
library(psych) # principal() 
library(factoextra) # fviz_pca_biplot()
```



## Q1 parallel analysis

### Read File

```{r}
data <- read.xlsx(xlsxFile="data/security_questions.xlsx", sheet = 2, colNames = TRUE)
```

### (a) Show a single visualization with scree plot of data, scree plot of simulated noise, and a horizontal line showing the eigenvalue = 1 cutoff.

```{r}
sim_noise_ev <- function(n, p) {
noise <- data.frame(replicate(p, rnorm(n)))
return( eigen(cor(noise))$values )
}

set.seed(42)
evalues_noise <- replicate(100, sim_noise_ev(dim(data)[1], dim(data)[2]))
```

```{r}
# draw
evalues_mean <- apply(evalues_noise, 1, mean)
pca <- prcomp(data, scale. = TRUE)
screeplot(pca, type="lines",col="brown3",main = "PCA variances",lwd=1.5,ylim = c(0, 10))
lines(evalues_mean,col="slateblue4" , type="b",lwd=1.5)
abline(h=1, lty="dotted")
legend("topright", c("Real data","Simulated Noise"),lty=c(1,1),col=c("brown3","slateblue4"))
```


### (b) How many dimensions would you retain if we used Parallel Analysis?

```{r}
eigenvalues <- eigen(cor(data))$values
sprintf("We should retain %d dimensions ", length(eigenvalues[eigenvalues>1]))
```

## Q2 Examine factor loadings

```{r}
dec_pca3_orig <- principal(data,nfactors = 3,rotate="none",scores = TRUE)
dec_pca3_orig
```


### (a) Looking at the loadings of the first 3 principal components, to which components does each item seem to best belong?

```{r}
dec_pca3_orig[["loadings"]]
```

+ It seems all components belongs to PC1.  
+ Take the threshold of loading to 0.5, `Q4`,`Q12`,`Q17`belongs to PC2.
+ Take the threshold of loading to 0.5, `Q5`,`Q10`belongs to PC3.  

### (b) How much of the total variance of the security dataset do the first 3 PCs capture?

**ANSWER:** $67%$ of variance captured from the first 3 PCs.

### (c) Looking at commonality and uniqueness, which items are less than adequately explained by the first 3 principal components?

**ANSWER:** According to the table, `Q2` is the least adequately explained component. The commonality of `Q2` is $1.035995$ and  uniqueness is $0.5394567$

### (d) How many measurement items share similar loadings between 2 or more components?

```{r}
fviz_pca_biplot(pca, invisible ="ind")+
 theme_minimal()
```
**ANSWER:** `Q1`,`Q4`,`Q12` share similar loadings between 2 or more components.

### (e) Can you distinguish a ‘meaning’ behind the first principal component from the items that load best upon it? (see the wording of the questions of those items)

**ANSWER:** Since the highest component of `PC1` is `Q1`,`Q14`, `Q18`, let's take a look at these question:

+ `Q1`:I am convinced that this site respects the confidentiality of the transactions received from me.  
+ `Q14`:This site devotes time and effort to verify the accuracy of the information in transit.  
+ `Q18`:This site uses some security controls for the confidentiality of the transactions received from me.

I would give a conclusion about the users care about how website protect the security.


## Q3 rotate the our principal component axes 

```{r}
dec_pca3_rot <- principal(data,nfactors = 3,rotate="varimax",scores = TRUE)
dec_pca3_rot
```



### (a) Individually, does each rotated component (RC) explain the same, or different, amount of variance than the corresponding principal components (PCs)?

**ANSWER:** The variance of RCs are **different** to original PCs.

### (b) Together, do the three rotated components explain the same, more, or less cumulative variance as the three principal components combined?

**ANSWER:** The cumulative variance 3 RCs is same to 3 PCs, which is 67%.

### (c) Looking back at the items that shared similar loadings with multiple principal components (#2d), do those items have more clearly differentiated loadings among rotated components?

**ANSWER:** According to the components of `RC1`, those items have more clearly differentiated loadings now.

### (d) Can you now interpret the “meaning” of the 3 rotated components from the items that load best upon each of them? (see the wording of the questions of those items)

**ANSWER:** Since the highest component of `RC1` is `Q7`,`Q9`,`Q11`, `Q14`, `Q16`, let's take a look at these question:

+ `Q7`:This site never sells my personal information in their computer databases to other companies   
+ `Q9`:I can remove my personal information from this site when I want to.  
+ `Q11`:This site devotes time and effort to preventing unauthorized access to my personal information.  
+ `Q14`:This site devotes time and effort to verify the accuracy of the information in transit.    
+ `Q16`:Databases that contain my personal information are protected from unauthorized access 

I would give a conclusion about the users care about the **personal information** should be protected well.


### (e) If we reduced the number of extracted and rotated components to 2, does the meaning of our rotated components change?

```{r}
dec_pca2_rot <- principal(data,nfactors = 2,rotate="varimax",scores = TRUE)
dec_pca2_rot
```

**ANSWER:**  Yes, the components in RC1 is acturally changed.


## (ungraded) Looking back at all our results and analyses of this dataset (from this week and previous), how many components (1-3) do you believe we should extract and analyze to understand the security dataset? Feel free to suggest different answers for different purposes.

**ANSWER:** According to the cumulative variance explained, I think 3 components is better to understand the security dataset.


## Reference Link
+ [Colors code in R](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf)
+ [screeplot: Draw a SCREE plot, showing the distribution of explained...](https://rdrr.io/bioc/PCAtools/man/screeplot.html)
+ [fviz_pca: Quick Principal Component Analysis data visualization - R software and data mining](http://www.sthda.com/english/wiki/fviz-pca-quick-principal-component-analysis-data-visualization-r-software-and-data-mining#fviz_pca_ind-graph-of-individuals)

