---
title: "Hw week9"
author: '106022103'
date: "2021/4/25"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assist
+ Helped by `106000199` 
  + Discussion of systematic and random error.
  + How to explain the problem 1-ii.
+ Helped by `106022213`
  + Discussion of type I and type II error in problem 1-b-iv
  + How to explain the converage error different to random or systemitic error in probelm 1-i.
+ Helped by `106070038`
  + The part of ANOVA test in problem 2-e.


## Set up 

### import libary

```{r import, message=FALSE, warning=FALSE}
library(ggplot2)
library(plyr)
require(qqplotr)
```


## Q1

## Q2

### Read file
```{r read file}
experiment <- read.csv('study2Data.csv', header=TRUE)
BY_data <- with(experiment, data.frame(Subject, Axis='BY', Emotion_Condition, ACC=BY_ACC, SAD_ESRI))
RG_data <- with(experiment, data.frame(Subject, Axis='RG', Emotion_Condition, ACC=RG_ACC, SAD_ESRI))

BY_data_sad <- BY_data[BY_data$Emotion_Condition == "Sadness",]
BY_data_neu <- BY_data[BY_data$Emotion_Condition == "Neutral",]
RG_data_sad <- RG_data[RG_data$Emotion_Condition == "Sadness",]
RG_data_neu <- RG_data[RG_data$Emotion_Condition == "Neutral",]

BY_data_sad$Group <- "BY_sad"
BY_data_neu$Group <- "BY_neu"
RG_data_sad$Group <- "RG_sad"
RG_data_neu$Group <- "RG_neu"
```


### (a) Visulize
```{r}
df <- rbind(BY_data_sad, BY_data_neu, RG_data_sad, RG_data_neu)
# get means of each group
mu <- ddply(df, "Group", summarise, grp.mean=mean(ACC))
# Visualize the density plot and add mean lines.
p <- ggplot(df, aes(x=ACC, color=Group)) +
  geom_density(lwd=1.2) +
  geom_vline(data=mu, aes(xintercept=grp.mean, color=Group),
             linetype="dashed",lwd=1) +
  labs(title="Density plot",x="Accuracy", y = "Density") + 
  theme(legend.position="bottom")
p
```

**ANSWER:** The `BY_data` is more concentrated than `RG_data`. The `RG_neu` group is the least concentrated.


### (b) Trational t-test  in blue-yellow accuracy between sad and neutral.

```{r 2b}
t.test(BY_data_sad$ACC, BY_data_neu$ACC, var.equal = FALSE, conf.level = 0.95)
```
**ANSWER:** Since the p-value $0.04309<0.05$, so we can reject $H_0$. It means that there is a significant difference in blue-yellow accuracy between sad and neutral participants at 95% confidence.



### (c) Trational t-test  in red-green accuracy between sad and neutral.

```{r 2c}
t.test(RG_data_sad$ACC, RG_data_neu$ACC, var.equal = FALSE, conf.level = 0.95)
```

**ANSWER:** Since the p-value $0.3833>0.05$, so we can NOT reject $H_0$. It means that there is NOT a significant difference in red-green accuracy between sad and neutral participants at 95% confidence.


### (d) (not graded) Do the above t-tests support a claim that there is an interaction between emotion and color axis? 

**ANSWER:** Not necessarily. While there is a significant difference between blue-yellow, there is not between red-green.


### (e) ANOVA 

```{r}
all_data <- rbind(BY_data, RG_data)
summary(aov(formula = ACC ~ Axis + Emotion_Condition + Axis:Emotion_Condition, data=all_data))
```

**ANSWER:** As shown by ANOVA, the significance level of `Emotion_Condition` was between $(0.05, 0.1)$.  
This means that if we change the applicable confidence level from $95\%$ to $90\%$, then we can say that color has a significant effect on emotion.


## Reference

+ [Random vs Systematic Error](https://www.physics.umd.edu/courses/Phys276/Hill/Information/Notes/ErrorAnalysis.html)